---
title: "homework_2_Fan_Chisun"
author: "Chisun  Fan"
date: "February 12, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

 


#3.2.4 Exercises

###Run ggplot(data = mpg). What do you see?

**A blank plots window showed up.**

###How many rows are in mpg? How many columns?

**There are 234 rows and 11 columns**

###What does the drv variable describe? Read the help for ?mpg to find out.

**The drv variable specifies the drivetrain of the car.**


###Make a scatterplot of hwy vs cyl.




```{r }
library(tidyverse)
library(mdsr)
```



```{r }
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = cyl, y = hwy))
```


###What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
```{r}
ggplot(data = mpg) + 
 geom_point(mapping = aes(x = class, y = drv))
```

**The plot is not useful because no quantitative information can be displayed.**

#Section 3.3.1: all exercises

###What’s gone wrong with this code? Why are the points not blue?

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
  
  
**To make all the points blue, color needs to be an argument of geom_point, not an aesthetic as in the current code.** 

### Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?


**Categorical: manufacturer, model, trans, drv, fl, and class**
 
**Continuous: displ, year,  cyl, cty, hwy**

###Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

**Using color: categorical mapped each category to different color. Continuous mapped to same color with differet transparency.**
**Using size : categorical come up with warning as not suggested. Continuous map size to the variable number.**
**Using shape : categorical maps each category to different shapes. continuous comes up with error as it can not be mapped to shape.**



###What happens if you map the same variable to multiple aesthetics?

**It appears to plot just fine. For example if I assign both y axis and size to hwy, it will plot large dots at higher y value, which shows redundent information.**



###What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

**The stroke aesthetic gives the width of the border. It only works with shape 21, 22, 23, and 24.**

###What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)? Note, you’ll also need to specify x and y.

**The aesthetic will be based on the logic value of the evaluation rather than the value of the variable.**

#Section 3.5.1:  #4 and #5 only

###Take the first faceted plot in this section:

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 2)
###What are the advantages to using faceting instead of the colour aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?

**It's more clear using faceting if the focus is on each value of an variable. but if the focus is on comparing differnt values of a variable or overall observation,  then color aesthetic will be a better choice. If the dataset is larger their maybe a lot of overlay and color aesthetic may not communicate the real information. Faceting will be become a better choice at that point.**


###Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol arguments?

**nrow gives number of rows. ncol gives number of columns. when both present, it will satisfy ncol first and may not reach the number of rows specified.**

**as.table, and dir options control the layout of the individual panels**

**facet_grid does not have nrow and ncol because row and column are already defined by "~".**


#3.6.1 Exercises

###What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?

**geom_line, geom_boxplot, geom_histogram, and geom_area**

###Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions.

ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
  
**Ran and showed as predicted.**

###What does show.legend = FALSE do? What happens if you remove it?

**No difference if removed in this situation. Because there is no legend pecified to the group. If there was a legend specified it will appear somewhere on the plot. **

### Why do you think I used it earlier in the chapter?

**Just in case to make sure no legend output on the plot.**

###What does the se argument to geom_smooth() do?

**Plot the confidence level, which is the shaded area on the plot.**

###Will these two graphs look different? Why/why not?

ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
  
**The two plots should look identical. But the second code section needs to load mpg data twice.**
  
###Recreate the R code necessary to generate the following graphs.

**1: ggplot(data=mpg, mapping=aes(x=displ, y=hwy))+geom_point()+geom_smooth()**

**2: ggplot()+geom_point(data=mpg, mapping=aes(x=displ, y=hwy))+geom_smooth(data=mpg,mapping=aes(x=displ, y=hwy,group=drv), se=FALSE)**

**3: ggplot()+geom_point(data=mpg, mapping=aes(x=displ, y=hwy,color=drv))+geom_smooth(data=mpg,mapping=aes(x=displ, y=hwy,group=drv), se=FALSE)**

**4: ggplot()+geom_point(data=mpg, mapping=aes(x=displ, y=hwy,color=drv))+geom_smooth(data=mpg,mapping=aes(x=displ, y=hwy), se=FALSE)**

**5: ggplot()+geom_point(data=mpg, mapping=aes(x=displ, y=hwy,color=drv))+geom_smooth(data=mpg,mapping=aes(x=displ, y=hwy,linetype=drv), se=FALSE)**

**6: ggplot()+geom_point(data=mpg, mapping=aes(x=displ, y=hwy,color=drv))**



#Section 3.7.1

###What does geom_col() do? How is it different to geom_bar()?

**They both generate bar charts. geom_bar makes the height of the bar based on the number of cases, no y aesthetic need to specified. geom_col leaves the data as is. y aesthetic need to be specified.**


#Look at the data graphics at the following link: What is a Data Scientist. Please briefly critique the designer’s choices. What works? What doesn’t work? What would you have done differently?


**The pie chart and bar chart works as intended, numbers with faded transparency marginally works. individual panels comparing DS and BI do not work. I would choose a consolidated bar chart to represent these information.**


 