---
title: "homework_3_Fan_Chisun"
author: "Chisun  Fan"
date: "February 15, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##3.8.1 Exercises

*1.What is the problem with this plot? How could you improve it?*

*ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +*
*geom_point()*
  
###Points are overlapped and not showing the complete data. Replace geom_point with geom_gitter will fix the overlapping issue and show every instance of the data set.  


*2.What parameters to geom_jitter() control the amount of jittering?*


###width and height


*3. Compare and contrast geom_jitter() with geom_count().*

```{r,warning=FALSE,message=FALSE}
library(tidyverse)
ggplot(data=mpg, mapping=aes(x=cty, y=hwy))+geom_count()
```


```{r,warning=FALSE,message=FALSE}
ggplot(data=mpg, mapping=aes(x=cty, y=hwy))+geom_jitter()
```

###geom_jitter shows overlapping data by jittering while geom_count shows overlapping data by the size of the point.

*4.What’s the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.*

###The default is "dodge2"

```{r,warning=FALSE,message=FALSE}
ggplot(data=mpg, mapping=aes(x=drv, y=hwy, fill=class))+geom_boxplot(position="identity")
```

```{r,warning=FALSE,message=FALSE}
ggplot(data=mpg, mapping=aes(x=drv, y=hwy, fill=class))+geom_boxplot()
```

##3.9.1 Exercises

*2.What does labs() do? Read the documentation.*

###The labs() function interpret the graphic information using labels, titles, and other text so that the audience can understand the plot better.

*4.What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?*

```{r,warning=FALSE,message=FALSE}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

###The plot shows a linear relation between city and highway mpg. coord_fixed ensure the ratio is 1 for both x and y  scales since city and highway mpg are using same unit. geom_abline plot a reference line with intercept and slope based on the data. 

##4.4 Practice

*1.Why does this code not work?*

*my_variable <- 10*

*my_varıable*

*> Error in eval(expr, envir, enclos): object 'my_varıable' not found*

*Look carefully! (This may seem like an exercise in pointlessness, but training your brain to notice even the tiniest difference will pay off when programming.)*

###Don't know. code executed just fine in my console sub-window.

```{r,warning=FALSE,message=FALSE}
my_variable <- 10
my_variable
```

*2.Tweak each of the following R commands so that they run correctly:*

library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)

filter(diamond, carat > 3)

###first two does not have issues running. 
###filter(mpg, cyl== 8)
###filter(diamonds, carat > 3)

##5.2.4 Exercises
*1.Find all flights that*

*1.Had an arrival delay of two or more hours*

```{r,warning=FALSE,message=FALSE}
library(nycflights13)
filter(flights, dep_delay >=120)
```

*2.Flew to Houston (IAH or HOU)*

```{r,warning=FALSE,message=FALSE}
filter(flights, dest == "IAH" | dest == "HOU")
```

*3.Were operated by United, American, or Delta*

```{r,warning=FALSE,message=FALSE}
filter(flights, carrier == "UA" | carrier == "AA" | carrier == "DL")
```

*4.Departed in summer (July, August, and September)*

```{r,warning=FALSE,message=FALSE}
filter(flights, month ==7 | month == 8 | month == 9)
```

*5.Arrived more than two hours late, but didn’t leave late*

```{r,warning=FALSE,message=FALSE}
filter(flights, (arr_delay > 120) & (dep_delay <= 0))
```

*6.Were delayed by at least an hour, but made up over 30 minutes in flight*

```{r,warning=FALSE,message=FALSE}
filter(flights, (dep_delay >= 60) & (arr_time - sched_arr_time < 30))
```


*7.Departed between midnight and 6am (inclusive)*

```{r,warning=FALSE,message=FALSE}
filter(flights, dep_time >= 0 & dep_time <=360)
```


*3.How many flights have a missing dep_time? What other variables are missing? What might these rows represent?*

###8255 flights have a missing dep_time. For those flights the dep_delay and arr_time are also missing. I would interpret them as cancelled flight since they do have sched_dep_time.

*4.Why is NA ^ 0 not missing? Why is NA | TRUE not missing? Why is FALSE & NA not missing? Can you figure out the general rule? (NA \* 0 is a tricky counterexample!)*

###anything to the power of 0 is always 1.
###anything or with a TRUE  is always TRUE.
###anything and with a FALSE  is always FALSE
###NA \* 0 is NA. On Quora the explanation is NaN*0=NaN where NaN stands for "Not a numerical value".

##5.4.1 Exercises
*1.Brainstorm as many ways as possible to select dep_time, dep_delay, arr_time, and arr_delay from flights.*

```{r,warning=FALSE,message=FALSE}
select(flights, starts_with("dep"), starts_with("arr"))

select(flights,dep_time,dep_delay,arr_time,arr_delay)

vars <- c("dep_time","dep_delay","arr_time","arr_delay") 
select(flights,vars)
```


*3.What does the one_of() function do? Why might it be helpful in conjunction with this vector?*

*vars <- c("year", "month", "day", "dep_delay", "arr_delay")*

###one_of matches name against any string in the vector. It is helpful because it is more interpretive using the function. In reality there is no difference with or without it.

###select(flights, vars) output the same result as select(flights, one_of(vars))

 