---
title: "COMPSCIX 415.2 Homework 9/Final"
author: "Chisun  Fan"
date: "March 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r,warning=FALSE,message=FALSE}
library(tidyverse)
library(broom)
```
 
 
Exercises (Total Points - 20)

##Exercise 1 - Sampling Distributions, Functions and For Loops (10 points)

Recall that the distribution of the sample mean is approximately a Normal distribution, and that the standard error is σn√. This holds true regardless of the distribution of our population.

For this problem, assume that the number of miles that a particular car can run before its battery wears out is exponentially distributed with an average of 10,000 miles. The exponential distribution looks like this:

The exponential distribution has a rate parameter that controls how quickly the distribution decays and defines what the mean and standard deviation will be. In our case the rate = 1/10000, the mean = 10000 and the  standard deviation = 10000. You can sample from this exponential distribution in R using this code:

sample size
samp_size <- 100
set the rate parameter
samp_rate <- 1/10000

take sample
rexp(n = samp_size, rate = samp_rate)
STEP 1

Write an R function that does the following:

Takes a sample of size samp_size from this exponential distribution (samp_size is an input parameter for the function)
Calculates the mean of that sample
Calculates the standard deviation of that sample
Returns the calculated mean and standard deviation as a list
Helper code

samp_fun <- function(samp_size, samp_rate) {
  
  ...your code here...
  
  stats <- list(samp_avg = samp_avg, samp_std_dev = samp_std_dev)
  return(stats)
}


```{r,warning=FALSE,message=FALSE}

samp_fun <- function(samp_size,samp_rate){

samples =  rexp(samp_size,rate=samp_rate)
samp_avg = mean(samples)
samp_std_dev = sd(samples)
stats <- list(samp_avg=samp_avg,samp_std_dev = samp_std_dev)
return(stats)
}
```


STEP 2

Then write a loop that does this:

Runs the above function 1000 times, with samp_size = 50 and samp_rate = 1/10000
Saves all of the sample means in a vector called sample_means, and all of the sample standard deviations in a vector called sample_sds

```{r,warning=FALSE,message=FALSE}

samp_means <- rep(NA,1000)
samp_sds <- rep(NA,1000)
samp_size <- 50
samp_rate <- 1/10000
for(i in 1:1000) {
 stats <-  samp_fun(samp_size,samp_rate)
 samp_means[i] <-stats$samp_avg
 samp_sds[i] <- stats$samp_std_dev
}
 
```


STEP 3

Then

plot your sample means as a histogram

```{r,warning=FALSE,message=FALSE}
as.data.frame(samp_means) %>% ggplot(mapping=aes(x=samp_means))+geom_histogram()
```

output the standard deviation of your sample means

```{r,warning=FALSE,message=FALSE}
 sd(samp_means)
```

calculate the theoretical standard error (σ=10000, n = sample size)

```{r,warning=FALSE,message=FALSE}

10000/sqrt(50)
```

calculate the mean of the sample standard deviations and use this to calculate the empirical standard error

```{r,warning=FALSE,message=FALSE}
mean_sd <- mean(samp_sds)
mean_sd/sqrt(50)
```

STEP 4

Repeat STEP 2 and STEP 3 using a sample size of 5000.

```{r,warning=FALSE,message=FALSE}
samp_means <- rep(NA,1000)
samp_sds <- rep(NA,1000)
samp_size <- 5000
samp_rate <- 1/10000
for(i in 1:1000) {
 stats <-  samp_fun(samp_size,samp_rate)
 samp_means[i] <-stats$samp_avg
 samp_sds[i] <- stats$samp_std_dev
}
 
```

plot your sample means as a histogram

```{r,warning=FALSE,message=FALSE}
as.data.frame(samp_means) %>% ggplot(mapping=aes(x=samp_means))+geom_histogram()
```

output the standard deviation of your sample means

```{r,warning=FALSE,message=FALSE}
 sd(samp_means)
```

calculate the theoretical standard error (σ=10000, n = sample size)

```{r,warning=FALSE,message=FALSE}

10000/sqrt(5000)
```

calculate the mean of the sample standard deviations and use this to calculate the empirical standard error

```{r,warning=FALSE,message=FALSE}
mean_sd <- mean(samp_sds)
mean_sd/sqrt(5000)
```

  

##Exercise 2 - Linear Regression (5 points)

For this exercise we will return to the House Prices prediction dataset that we used for HW 7. You should have already downloaded the train.csv dataset before, but if you didn’t you can download it from Canvas in this week’s module.

Load the train.csv dataset into R and fit a regression model with:

y = SalePrice
Features: LotArea, OverallQual, and ExterQual
Answer these questions:

Use the broom package to output the coefficients and the R-squared
 

```{r,warning=FALSE,message=FALSE}
File_path <- "C:/users/chisun/downloads/train.csv"
train_csv <- read_delim(File_path,',')
fit <- lm(SalePrice ~ LotArea+OverallQual+ExterQual, data = train_csv)
summary(fit)
tidy(fit)
glance(fit)
```

Interpret the coefficient on LotArea

**The coefficient 1.45 indicates the value per square foot of lot size** 

Interpret the coefficient on ExterQualGd

**The coefficient -70000 is salePrice adjustment from the mean value when external grade is Gd.** 

Compare this model to the model we fit in HW 7 with GrLivArea, OverallQual, Neighborhood. Which is the better fitting model?

**HW 7 appeared to be a better model because the R value is higher. Both models are good since the P values are small.**

##Exercise 3 - AB Testing (5 points)

Download the ab_test_data.csv file from Canvas. This file contains two columns: version and conversion. Each row is a visitor to a webpage. The version column tells us which version of the webpage the visitor saw, and the  conversion column is a binary value and equals 1 if the visitor converted (0 otherwise).

We want to perform an AB test on this data to see if the conversion rates are different for the two versions of the webpage.

Answer these questions:



```{r,warning=FALSE,message=FALSE}
File_path <- "C:/users/chisun/downloads/ab_test_data.csv"
data_csv <- read.csv(File_path)
A_total <- nrow(filter(data_csv,version == 'A'))
B_total <- nrow(filter(data_csv,version == 'B'))
A_convert <- nrow(filter(data_csv,version == 'A' & conversion == 1))
B_convert <- nrow(filter(data_csv,version == 'B' & conversion == 1))
A_convert/A_total
B_convert/B_total
two_prop_test <- prop.test(c(A_convert,B_convert),c(A_total,B_total))
two_prop_test

```

What proportion of visitors converted for each version of the webpage?

**Around  4 percent for A and 10 percent for B.**


Perform the AB test in R. What is the p-value for the AB test (hypothesis test of proportions)?

**P value is extermely small. which indicates the conversion rate is reliable.**






 
 
